Analysis of Bauer et al. (unpublished) Field experiment: <br> Persistence

### 2022-12-07 R/model_fcs_check.Rmd
Refer to BARG framework

Analysis guided by
<br>
Reporting: Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
<br>
Model check: Gabry et al. (2019) J R Stat Soc A Stat [DOI: 10.1111/rssa.12378](https://doi.org/10.1111/rssa.12378)
<br>
Priors: Lemoine (2019) Oikos [DOI: 10.1111/oik.05985](https://doi.org/10.1111/oik.05985)
<br>
Model check: Deapoli & Schoot (2017) Psychol Methods [DOI: 10.1037/met0000065](https://doi.org/10.1037/met0000065)

@@

#### Packages

@@

### Load models

@@

```{r load-models collapse = TRUE}
load(file = here("outputs", "models", "model_fcs_2.Rdata"))
load(file = here("outputs", "models", "model_fcs_full.Rdata"))
m_1 <- m2
m_2 <- m_full
```

@@

### Coefficient of determination (<i>R</i>²)

@@

@@

#### Prior summary

@@

#### Rhat

@@

#### Effective sampling size (ESS)

@@

### Posterior predictive check

@@

## Output of choosen model

### Model output

Conditional and marignal <i>R</i>²

```{r conditional-marginal-r2 collapse = TRUE}
brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot)) 
brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
```

Posteriors of chosen model

```{r posterior-chosen-model}
draws1
mcmc_intervals(
  posterior1,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```

Posteriors of second model:

```{r posterior-second-model}
mcmc_intervals(
  posterior2,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```

@@

Just, to get exact values if necessary, which is not possible from the figure

@@

# Session info

>>>>

Analysis guided by
<br>
Bayesian analysis reporting guidelines (BARG): Kruschke (2021) Nat Hum Behav [DOI: 10.1038/s41562-021-01177-7](https://doi.org/10.1038/s41562-021-01177-7)
<br>
Model check: Gabry et al. (2019) J R Stat Soc A Stat [DOI: 10.1111/rssa.12378](https://doi.org/10.1111/rssa.12378)
<br>
Priors: Lemoine (2019) Oikos [DOI: 10.1111/oik.05985](https://doi.org/10.1111/oik.05985)
<br>
Model check: Deapoli & Schoot (2017) Psychol Methods [DOI: 10.1037/met0000065](https://doi.org/10.1037/met0000065)

@@

#### Packages (BARG 2.A)

@@

### Load models (BARG 1.D/6.G)

@@

```{r load-models collapse = TRUE}
load(file = here("outputs", "models", "model_fcs_2.Rdata"))
load(file = here("outputs", "models", "model_fcs_full.Rdata"))
# BARG 5
load(file = here("outputs", "models", "model_fcs_2_flat.Rdata"))
# BARG 1.E
load(file = here("outputs", "models", "model_fcs_2_prior.Rdata"))
m_1 <- m2
m_2 <- m_full
```

### Model comparison

@@

@@

#### Bayes factor (BARG 3.C)

```{r}
brms::bayes_factor(m_1, m_2)
```

@@

#### Prior summary (BARG 1.D)

@@

#### Rhat (BARG 2.B)

@@

#### Effective sampling size (ESS) (BARG 2.C)

@@

### Posterior predictive check (BARG 3.A)

@@

## Posterior distributions (BARG 3.B)

### Forest plot

Chosen model:

```{r posteriors-chosen-model}
mcmc_intervals(
  posterior1,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```

Second model:

```{r posteriors-2nd-model}
mcmc_intervals(
  posterior2,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```

@@

Effect sizes of chosen model just to get exact values of means etc. if necessary.

@@

# Session info (BARG 2.A/6.A/6.B)

### 2022-12-07 R/model_persistence_check.Rmd
Refer to BARG framework

```{r collapse = TRUE, message = FALSE}
load(file = here("outputs", "models", "model_persistence_2.Rdata"))
load(file = here("outputs", "models", "model_persistence_full.Rdata"))
m_1 <- m2
m_2 <- m_full
```

@@

## Output of choosen model

### Model output

Conditional and marignal <i>R</i>²

```{r collapse = TRUE}
brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot)) 
brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
```

Posteriors of chosen model

```{r}
draws1
mcmc_intervals(
  posterior1,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```

Posteriors of second model:

```{r}
mcmc_intervals(
  posterior2,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```

>>>>

```{r collapse = TRUE, message = FALSE}
load(file = here("outputs", "models", "model_persistence_2.Rdata"))
load(file = here("outputs", "models", "model_persistence_full.Rdata"))
# BARG 5
load(file = here("outputs", "models", "model_persistence_2_flat.Rdata"))
# BARG 1.E
load(file = here("outputs", "models", "model_persistence_2_prior.Rdata"))
m_1 <- m2
m_2 <- m_full
```

### Model comparison

@@

## Posterior distributions (BARG 3.B)

### Forest plot

Chosen model:

```{r posteriors-chosen-model}
mcmc_intervals(
  posterior1,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```

Second model:

```{r posteriors-2nd-model}
mcmc_intervals(
  posterior2,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```
